Application of PID controller and CNN to control Duckiebot robot

### 2023-09-13 article-en.tex
English abstract correction

\begin{abstract}

\end{abstract}

>>>>

\begin{abstract}
The paper presents the design and practical implementation by students of a control system
using a classical PID controller and a controller using artificial neural networks.
The control object is a Duckiebot robot, and the task it is to perform is to drive the robot along a designated line (\emph{line follower}). The purpose of the proposed activities is to familiarize students with the advantages and disadvantages of the two controllers used and to acquire the ability to implement control systems in practice. 
The article briefly describes how the two controllers work, how to practically implement them, and how to practically implement the exercise. 
\end{abstract}
